%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
% PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[margin, 10pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above

\setlength{\textwidth}{5.1in} % Text width of the document

\begin{document}

%----------------------------------------------------------------------------------------
% NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------

\moveleft.5\hoffset\centerline{\large\bf Neal Edward Elliott Sr.} % Your name at the top

\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'

\moveleft.5\hoffset\centerline{2070 Ingleside Ct} % Your address
\moveleft.5\hoffset\centerline{Crofton, MD 21114}
\moveleft.5\hoffset\centerline{(443) 694-1060}
\moveleft.5\hoffset\centerline{nealelliott@netscape.net}
\moveleft.5\hoffset\centerline{https://binary-janitor.com}

%----------------------------------------------------------------------------------------

\begin{resume}

%----------------------------------------------------------------------------------------
% Technology SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{TECHNOLOGY \\ SKILLS}

{\sl \textbf{Programming Languages:}} Bash, Tcl/TK, expect, Perl, C, YAML, PHP, JavaScript, Java. \\
{\sl \textbf{Operations Technologies:}} Docker, Jenkins, Ansible, Vagrant, OpenSMTPD, git. \\
{\sl \textbf{Third Party Integrations:}} S3, OpenLDAP (LDAP), FreeIPA (LDAP), OpenDirectory (LDAP) \\
{\sl \textbf{Cloud Providers:}} AWS, GCE, VMWare vsphere. \\
{\sl \textbf{Operating Systems:}} MacOS, Windows 10, GNU/Linux (Debian / CentOS), OpenBSD, NetBSD, FreeBSD, AIX, Solaris. \\
{\sl \textbf{Embedded Engineering:}} Raspberry Pi, Arduino. \\
{\sl \textbf{Education:}} B.S. in computer science from UMGC\\
{\sl \textbf{Clearance:}} TS/SCI \\

%----------------------------------------------------------------------------------------
% PROFESSIONAL EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{EXPERIENCE}
{\sl Software Developer } \hfill 2021-Present \\
Peraton
\begin{itemize}
  \item Maintain custom software through automation using Ansible
  \item Troubleshoot and identify vulnerabilities, in applications
\end{itemize}

{\sl Sr. System Administrator } \hfill 2020-2021 \\
Peraton
\begin{itemize}
  \item Worked as a developer in an Agile scrum team to write ansible playbooks to automate software installs
  \item Designed, and implemented a central syslog solution using rsyslog
  \item Built an internal webhosted CentOS RPM repository to maintain current patches of operational VMs
  \item built a website using PHP to help users change their passwords on both LDAP and Active Directory account management systems
  \item Planned and implemented migration of Solaris ClearCase source code repository into a modern CentOS ClearCase version
  \item built customized RPMS, and windows NSIS installer to install in-house software
\end{itemize}

{\sl System Administrator } \hfill 2006-2020 \\
Northrop Grumman Corporation
\begin{itemize}
  \item Supporting and maintaining enterprise level data center servers on a distributed network
  \item Experience with VMware vSphere, and ESXi server
  \item Experience with Isilon’s Onefs
  \item Ported a Solaris version of Nagios which included apache/PHP dependencies
  \item Designed and documented storage (RAID) solutions for servers
  \item Built custom Solaris packages, and Linux RPMS out of freeware COTS products
  \item Proactively tunes systems to limit performance problems
  \item Scans systems using SECSCAN and harden them based off of the scan results
  \item Provide level 2 and 3 SME support for multiple Solaris systems that are located worldwide
  \item Support application development during the software development life cycle
  \item Develop scripts using expect to automate system transitions
  \item Troubleshoot and identify OS and software related issues by using truss and collecting various system logs
  \item Resolves network related problems such as correcting VLAN assignments
  \item Troubleshoots and corrects network performance problems
  \item Designed a backup solution by using Open Source software AMANDA
  \item Developed a script to automate router backups on over 100+ routers nightly
  \item Proficient in C, TCL/TK, Java, expect and Perl
  \item Documents install procedures for baseline system configurations
  \item Built custom jumpstart Solaris 10 install DVDs for automated installs
  \item Writes software fixes for custom server releases
  \item Uses ZFS and disk suite for various raid level configurations
\end{itemize}

{\sl Mission System Engineer } \hfill 2004-2006 \\
Honeywell
\begin{itemize}
  \item Provide system software support for Linux, IRIX, Solaris and AIX systems
  \item Developed shell scripts to automate account management on various UNIX platforms
  \item Planned and configured High Availability Cluster Management for AIX 5.2 servers
  \item Developed a full backup and restore plan for Linux, AIX and IRIX systems
  \item Run network security scans to audit system vulnerability
  \item Configured a system log server that consolidates system logs to two IRIX servers
  \item Designed a script that emails system administrators when host is unreachable
  \item Supported deployment Teams at White Sands NM, Fairbanks AK, Wallops VA, Svalbard Norway and Goddard Space Flight Center
  \item Configured gigabit network for several CIDR /27 networks
\end{itemize}

{\sl Solaris System Administrator} \hfill 2003-2004 \\
Mori Associates
\begin{itemize}
  \item Lead UNIX system administrator Responsible for all of the UNIX machines on the NIDDK/NIH campus
  \item Scheduled system outages for patch installs
  \item Detailed troubleshooting of hardware, software, and network related issues
  \item Manage and maintain system level security
  \item Ensured patch level of each OS
  \item Responsible for the following operating systems; IRIX, Linux, Solaris and AIX
  \item Developed backup scripts for numerous machines
  \item Worked closely on computing problems with the researchers at the National Institute of Health
  \item Support mathmatica, Maple and many other NIH based applications
  \item Wrote custom applications in C, Tcl/Tk and perl
\end{itemize}

{\sl System Engineer/Consultant } \hfill 2003-2003 \\
IT-CNP
\begin{itemize}
  \item Implemented a High Availability Cluster using two Dell Power edge servers running Red hat advanced server 2.0.  The cluster shared a Dell power vault disk array for storage of the highly available postgres database. The servers are used for traffic monitoring in the Maryland/DC area.
\end{itemize}

{\sl UNIX System Administrator } \hfill 1998 - 2003 \\
Honeywell Technology Solutions, Inc.
\begin{itemize}
  \item Implemented various software development lifecycle patterns to decrease development times and improve the speed at which software was deployed to production across many teams.
  \item UNIX system administrator for approximately 200 machines with operating systems TRU64, IRIX, AIX, Linux, Solaris, FreeBSD, OpenBSD, Mac-OS, Cisco IOS 11, OS/2 warp, vxworks, and Windows (all versions).
  \item Configured and maintained Cisco catalyst and 7500 series routers.
  \item Installed and used Tivoli Netview.
  \item Setup and built a High Availability Cluster Management (HACMP) for AIX.
  \item Installed and configured Legato Networker for a network backup system.
  \item Designed FDDI and 10BaseT networks, Domain Name Servers (DNS) and IRIX web servers.
  \item Installed and maintained Lighthouse matrix switches
  \item Developed shell scripts for system management, programs in C, TCL/TK Java programming, C++ programming, and Distributed Computing Environment (DCE).
  \item Troubleshot network problems.
  \item Responsible for securing multiple types of UNIX systems.
  \item Traveled to Alaska, White sands test facility in New Mexico and Norway to install ground stations for NASA's EDOS Project.
  \item Tested data links between Norway and NASA Goddard space flight center for real-time satellite data capture.
  \item Certified Linux administrator.
  \item Wrote custom UNIX scripts for TRW engineers.
  \item Traveled to South Boston to test the software on the central artery tunnel also known as Big Dig.
\end{itemize}

{\sl Lead System Administrator } \hfill 2000 - 2003 \\
IntelliObjects
\begin{itemize}
  \item Implemented web application security standards defined by OWASP.
  \item Developed and built the company network.
  \item Created the DNS server and coordinated the domain name registration.
  \item Installed and configured the company mail server.
  \item Configured and built apache for the company web server.
  \item Designed and installed the network firewall.
\end{itemize}

{\sl Electronic Maintenance Tech 2 } \hfill Jan 1997 - 1998 \\
Honeywell Technology Solutions, Inc.
\begin{itemize} \itemsep -2pt % Reduce space between items
  \item Supported the Earth Data Observation System (EDOS) Project.
  \item Assisted installation of a level zero processing facility (LZPF), upgraded, monitored, maintained and Repaired IBM RS/6000, SUN, SGI, PC's, and Mac equipment.
  \item Built and tested N-type and BNC cables.
  \item Configured, tested, maintained, and repaired Wan Router/Matrix Switches.
  \item Maintained and tested Lighthouse matrix switches.
  \item Configured and provide routine maintenance of Ampex DIS 160i tape drives.
  \item Installed Cisco Catalyst.
  \item Other duties as assigned.
\end{itemize}

{\sl Electronic Tech 1} \hfill Dec 1996 - 1997\\
Honeywell Technology Solutions, Inc.
\begin{itemize}
  \item Troubleshot, built, and configured computer systems.
  \item Installed and fabricated ceiling mounted TV's.
  \item Installed breaker panels for expansion.
  \item Added electrical outlets for new computer installs
  \item Installed circuit Breakers for computer equipment.
  \item Installed uninterruptible power supplies that were various sizes
  \item Built and tested RJ45 and coax cables.
  \item Disassembled 3-meter satellite tracking antenna in semi valley California.
  \item Develop plans to fabricate mounts or stands for uniquely shaped devices.
\end{itemize}

%----------------------------------------------------------------------------------------

\end{resume}
\end{document}
